---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
[![BCDevExchange Status](https://assets.bcdevexchange.org/images/badges/exploration.svg)](https://github.com/BCDevExchange/docs/blob/master/discussion/projectstates.md)
[![Travis Build Status](https://www.travis-ci.com/poissonconsulting/nrp.svg?token=LCuTqqVUfUECxm1xTQLb&branch=master)](https://www.travis-ci.com/poissonconsulting/nrp)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/nf8qrbm7imvkuj0q?svg=true)](https://ci.appveyor.com/project/joethorley/nrp)
[![codecov](https://codecov.io/gh/poissonconsulting/nrp/branch/master/graph/badge.svg?token=BYPzzOPDrd)](https://codecov.io/gh/poissonconsulting/nrp)

# nrp

`nrp` is an R package that is being developed for the Nutrient Restoration Program (NRP).
It currently provides the following functionality for CTD data:

**Read in raw data files**<br />
  The package checks the validity of input data, and references the the CTD site table in the database to ensure   the correct SiteID is assigned for each file. the date and units are extracted from the file metadata, and any   missing units are filled in.

**Upload data to the NRP SQLite database**<br />
  When uploading new data to the database, the package checks to ensure that no duplicate data is present,        that values fall within acceptable ranges, and that units are correct.

**Download CTD data**<br />
  CTD data can be downloaded from the database with optional filtering by SiteID, date range, and parameter       name. The CTD site table can also be downloaded from the database.

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/nrp)
```
# install.packages("drat")
drat::addRepo("poissonconsulting")
devtools::install_github("poissonconsulting/nrp")
```
## Demonstration

For simplicity, this demo uses an empty, temporary database to read and write to, and uses some test data that travels with the package.

```{r}
library(nrp)

# create empty database with automatically populated Site and Lake tables
# path = ":memory:" creates a temporory, in memory database
conn <- nrp_create_db(path = ":memory:", ask = FALSE) 

# provide a path to a .cnv file
path <-  system.file("extdata", "ctd/2018/KL1_27Aug2018008downcast.cnv",
                       package = "nrp", mustWork = TRUE)

# read in file
# function looks at the database site table to assign SiteID for each file
data <- nrp_read_ctd_file(path, db_path = conn)

data

# upload data to the database
nrp_upload_ctd(data = data, db_path = conn)

# download data from database, filtering by Date and SiteID
db_data <- nrp_download_ctd(start_date = "2018-08-27",
                            end_date = "2018-08-27",
                            sites = "KL1",
                            db_path = conn)
db_data
```

## Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/poissonconsulting/nrp/issues/).

## How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). 
By participating in this project you agree to abide by its terms

## License

The code is released under the Apache License 2.0

    Copyright 2015 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
