---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/poissonconsulting/nrp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/nrp/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/nrp/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/nrp)
[![Apache license](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)
<!-- badges: end -->

# nrp

`nrp` is an R package developed for the Nutrient Restoration Program (NRP).
It currently provides the following functionality for CTD and EMS data:

**Read in raw data files**<br />
  The package checks the validity of input data and does some cleaning and manipulation to make the data more informative and useful to the user.
  
  For CTD data, the date and parameter units are extracted from the file meta data. The SiteID is pulled from the raw data filename, and validated by cross referencing it to known sites in the database.

**Upload data to the NRP SQLite database**<br />
  When uploading new data to the database, the package checks to ensure that no duplicate data is present, and numerous checks are performed to ensure that the data's structure is correct and compatible with the database.

**Download CTD data**<br />
  Data can then be downloaded from the database with optional filtering by SiteID, date range, etc.

## Installation

To install the latest version from [GitHub](https://github.com/poissonconsulting/nrp)
```r
# install.packages("remotes")
remotes::install_github("poissonconsulting/nrp")
```

## Demonstration

For simplicity, this demonstration uses the function `nrp_create_db` to create an empty, temporary database to read and write to, and uses some test data that travels with the package. When connecting to a proper database, just provide the file path to the database for the argument `db_path` in all function calls and the connection will be made automatically. Alternatively you can connect to a database in R and then supply that connection object for the argument `db_path`.

```{r}
library(nrp)

# create empty database
# path = ":memory:" creates a temporary, in memory database
conn <- nrp_create_db(path = ":memory:")

# provide a path to a .cnv file
path <- system.file("extdata", "ctd/2018/KL1_27Aug2018008downcast.cnv",
  package = "nrp", mustWork = TRUE
)

# read in file
ctd_data <- nrp_read_ctd_file(path, db_path = conn)

# upload data to the database
nrp_upload_ctd(data = ctd_data, db_path = conn)

# download data from database, filtering by Date and SiteID and parameter
db_ctd_data <- nrp_download_ctd(
  start_date = "2018-08-27",
  end_date = "2018-08-27",
  sites = "KL1",
  parameters = "all",
  db_path = conn
)
```

There are additional functions in the nrp package that allow for easy downloading of other tables in the database.

```{r}
# Lakes and BasinArm tables
lakes <- nrp_download_lakes(db_path = conn)
basinArm <- nrp_download_ctd_basin_arm(db_path = conn)

# site table
sites <- nrp_download_sites(db_path = conn)

# ctd visit table
ctd_visit <- nrp_download_ctd_visit(db_path = conn)

# Tip: the nrp functions can also use global options to automatically know
# what database to connect to. Once you've set the global option "nrp.db_path"
# for the database you want to connect to, you don't have to provide
# the db_path argument any more within that R session

options(nrp.db_path = conn) # "conn" can also be a file path to a database

# now we can do things like:
lakes <- nrp_download_lakes()


# we conclude the demo by closing the database connection
# If you are providing a file path to the database, you do not need to do this
readwritesqlite::rws_disconnect(conn)
```

## Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/poissonconsulting/nrp/issues/).

## How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

## Code of Conduct

Please note that the nrp project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## License

The code is released under the Apache License 2.0

    Copyright 2019 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
